---
title: Working with large data
vignette: >
  % \VignetteIndexEntry{Working with large data}
  % \VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
output:
  html_document:
    mathjax: null   
---

```{r setup, include=FALSE}
rm(list = ls())
gc()
knitr::opts_chunk$set(echo = TRUE, cache = TRUE)
library(BiocStyle)
```

## Motivation 

Advances in scRNA-seq technologies have increased the number of cells that can 
be assayed in routine experiments.
Public databases such as [GEO](https://www.ncbi.nlm.nih.gov/geo/) are continually
expanding with more scRNA-seq studies, 
while large-scale projects such as the
[Human Cell Atlas](https://www.humancellatlas.org/) are expected to generate
data for billions of cells.
For effective data analysis, the computational methods need to scale with the
increasing size of scRNA-seq data sets.
This section discusses how we can use various aspects of the Bioconductor 
ecosystem to tune our analysis pipelines for greater speed and efficiency.

## Interoperability with popular single-cell analysis ecosytems

```{r message = FALSE}
library(Seurat)
library(SeuratData)
```
